% ============================================================
\section{Introduction}
\label{sec:introduction}
% ============================================================

Corporate treasury departments face an investment problem that differs from
standard portfolio optimisation.
Firms hold cash for precautionary motives, transaction needs, and financial
flexibility \citep{bates2009}, and survey evidence shows that corporate financial
decisions are shaped by liquidity, risk management, and governance constraints
\citep{graham2001}.
For these investors, the relevant benchmark is not simply the highest attainable
return, but a strategy that can preserve capital through severe market stress
while earning a return above low-risk cash instruments.
This creates a narrow design space: money-market instruments and short-duration
government bonds may offer insufficient real returns, while passive equity
exposure exposes the treasury portfolio to drawdowns that are difficult to
reconcile with corporate liquidity mandates.

Tactical asset allocation (TAA) offers a potential middle ground.
By rotating systematically across asset classes, TAA strategies seek to
participate in persistent return trends while reducing exposure during adverse
market regimes.
The empirical literature documents momentum effects across equities and across
asset classes \citep{jegadeesh1993, moskowitz2012, asness2013}, and trend-based
allocation rules have been shown to improve drawdown profiles in diversified
portfolios \citep{faber2007, antonacci2014}.
However, much of this literature is framed around individual investors, hedge
funds, or institutional portfolio management.
Less attention has been paid to the specific treasury problem: a rule-based,
fully automated strategy with monthly liquidity, no leverage or derivatives, and
a hard maximum drawdown constraint.

This paper develops and tests such a strategy.
The proposed allocation rule combines three components.
First, a multi-period momentum score averages 1-, 3-, 6-, and 12-month signals
to reduce dependence on any single lookback horizon.
Second, a minimum-correlation triplet selection rule implements the central
diversification insight of modern portfolio theory \citep{markowitz1952} by
holding three low-correlation assets among the eligible momentum candidates.
Third, a market-breadth crash filter, inspired by breadth-based defensive
allocation frameworks \citep{keller2017}, overrides the momentum allocation when
the equal-weighted risky universe experiences a broad monthly decline.
In that state, the portfolio reallocates to long-duration treasuries and
intermediate-duration treasuries or, if necessary, to cash.

We evaluate the strategy on a universe of 15 diversified ETFs covering global
equities, real estate, commodities, and fixed income from January 2008 to
December 2025.
The empirical design uses a strict temporal split: 2008--2019 for parameter
selection and 2020--2025 for out-of-sample evaluation.
This period includes the Global Financial Crisis, the COVID-19 crash, the 2022
inflation and rate shock, and the April 2025 tariff shock, providing several
distinct stress regimes in which to test the drawdown-control mechanism.
We also construct a UCITS-compliant European implementation to assess whether the
strategy can be translated into instruments available to European entities.

The main result is that the strategy satisfies the corporate drawdown constraint
while delivering equity-like returns.
Over 2008--2025 it achieves a CAGR of 11.47\%, a Sharpe ratio of 0.974, and a
maximum drawdown of $-13.79\%$.
Out-of-sample performance over 2020--2025 remains comparable, with a CAGR of
12.54\% and a maximum drawdown of $-10.84\%$.
The crash filter is economically important: during the Global Financial Crisis
the strategy gains $+17.64\%$ while the S\&P 500 loses $-33.05\%$.
The UCITS implementation achieves a gross CAGR of 12.71\% over March 2019--March
2026, with an estimated net CAGR of 12.35\% in the transaction-cost window.

The paper contributes to the literature in two ways.
First, it reframes TAA as a corporate cash-management problem rather than a
generic return-enhancement exercise.
Second, it shows that a simple breadth-based crash filter can materially improve
drawdown control when combined with momentum and correlation-based selection.
The resulting strategy remains transparent, reproducible, and implementable with
monthly ETF trades, making it compatible with the operational constraints of
corporate treasury.

The remainder of the paper is structured as follows.
Section~\ref{sec:literature} reviews the relevant literature.
Section~\ref{sec:methodology} describes the strategy design and data.
Section~\ref{sec:results} reports in-sample, out-of-sample, crisis-period, and
robustness results.
Section~\ref{sec:discussion} discusses the economic mechanism and practical
implications.
Section~\ref{sec:conclusion} concludes.
