% ============================================================
\section{Literature Review}
\label{sec:literature}
% ============================================================

\subsection{Portfolio Theory and Rule-Based Allocation}

Modern portfolio theory establishes diversification as the central mechanism for
reducing portfolio risk.
\citet{markowitz1952} show that portfolio choice depends not only on expected
returns and variances, but also on the covariance structure among assets.
This insight is directly relevant for multi-asset ETF allocation: a portfolio
formed from individually attractive assets can still be fragile if those assets
share the same downside exposure.
Later allocation frameworks, such as Black-Litterman \citep{black1992}, address
the instability of expected-return estimation by combining equilibrium returns
with investor views, but they still require modelling assumptions that may be
difficult to govern in a corporate treasury setting.

Rule-based TAA offers a different route.
Instead of estimating a full set of expected returns and covariances, the
allocation is driven by transparent signals, fixed eligibility criteria, and
predefined rebalancing rules.
Our strategy remains connected to the diversification logic of
\citet{markowitz1952} through its minimum-correlation triplet rule, but avoids
mean-variance optimisation and the associated sensitivity to estimated inputs.
This is important for implementation: a corporate user must be able to explain
why the portfolio changed, not only observe that an optimiser produced a new
weight vector.

\subsection{Momentum and Trend Following Across Asset Classes}

Momentum is one of the most extensively documented regularities in financial
markets.
\citet{jegadeesh1993} document cross-sectional momentum in equities, showing
that past winners tend to outperform past losers over intermediate horizons.
\citet{moskowitz2012} extend the evidence to time-series momentum across futures
markets, finding that an asset's own past return predicts its subsequent return
across equities, bonds, currencies, and commodities.
\citet{asness2013} further show that momentum is present across asset classes
and geographies, suggesting that the phenomenon is not confined to a single
market segment.

This literature provides the empirical basis for momentum-based asset rotation.
For long-only TAA, \citet{faber2007} shows that a simple moving-average rule can
improve drawdowns in a diversified asset portfolio, while \citet{antonacci2014}
popularises dual momentum, combining relative momentum across assets with an
absolute trend filter.
Our approach follows the same broad logic but differs in two respects.
First, momentum is measured through a multi-period score based on 1-, 3-, 6-,
and 12-month returns, reducing dependence on a single horizon.
Second, asset selection is not based solely on rank: among eligible assets, the
portfolio chooses the lowest-correlation triplet, explicitly linking trend
following with diversification.

\subsection{ETF-Based Tactical Asset Allocation}

Exchange-traded funds make systematic multi-asset allocation operationally
feasible because they provide liquid exposure to broad asset classes at low cost.
Several studies examine ETF-based or global asset-allocation strategies that
combine momentum, trend following, and risk control.
\citet{clare2016} show that trend following and momentum can improve global asset
allocation when combined with risk-parity ideas.
\citet{bellu2020} propose Protected Adaptive Asset Allocation, a momentum-based
framework that shifts toward cash protection during adverse conditions.
\citet{yang2019} analyse tactical allocation rules while emphasising the risk of
data snooping, an issue that is particularly relevant for parameter-rich
backtests.

Recent work continues to support the relevance of momentum for global allocation.
\citet{wu2017} study momentum in a strategic asset-allocation framework and show
that momentum changes optimal demand relative to myopic allocation.
\citet{wouassom2022} document global momentum effects across international equity
markets, and \citet{vukovic2023} report time-series momentum evidence for
European equity indices.
These papers motivate the use of momentum as a systematic signal, but they do
not address the specific corporate treasury objective of maintaining a hard
drawdown ceiling while avoiding leverage and derivatives.

\subsection{Crash Detection and Drawdown Management}

Momentum strategies can perform poorly around sharp reversals and early recovery
periods.
\citet{daniel2016} document momentum crashes and show that losses can cluster in
panic states and rebounds.
This creates a direct problem for corporate cash management: a strategy that
delivers attractive average returns but fails during abrupt market transitions
does not satisfy the treasury mandate.

Breadth-based defensive signals offer one response to this problem.
\citet{keller2017} introduce breadth momentum in the Vigilant Asset Allocation
framework, using the fraction of assets with positive momentum as a warning
indicator for defensive allocation.
Our crash filter adapts the same intuition in a simpler form.
Rather than measuring the number of assets with positive momentum, it monitors
the equal-weighted monthly return of the risky universe.
When the universe falls broadly enough in a single month, the model treats the
move as systemic stress and reallocates defensively.

Other downside-control approaches use explicit risk optimisation.
\citet{guo2023}, for example, combine time-series momentum with conditional
value-at-risk constraints and show improvements in downside-adjusted
performance.
Our contribution is deliberately simpler: the crash-control mechanism is a
monthly rule rather than an optimisation problem.
This makes the strategy easier to audit and more compatible with governance
processes in corporate treasury.

\subsection{Corporate Cash Management}

The corporate finance literature explains why firms hold cash but provides less
direct guidance on how excess cash should be invested once liquidity needs are
met.
\citet{bates2009} document a long-run increase in corporate cash holdings and
relate it to precautionary motives, changing firm characteristics, and cash-flow
risk.
\citet{graham2001} show that corporate financial decisions in practice are shaped
by risk management, flexibility, and managerial constraints, not only by
textbook value-maximisation models.

This paper connects those corporate finance concerns with the TAA literature.
The objective is not to propose a replacement for operating cash or legally
restricted liquidity reserves.
Instead, we evaluate whether a transparent, monthly, ETF-based allocation rule
can be used for a portion of strategic corporate cash where the firm seeks a
higher return than cash instruments while imposing a strict drawdown limit.
That framing distinguishes the strategy from generic wealth-management TAA and
defines the empirical tests reported below.
