% ============================================================
\section{Discussion}
\label{sec:discussion}
% ============================================================

\subsection{Why the Crash Filter Adds Value}

The central result of this paper is that the market-breadth crash filter generates
the largest single performance increment (Table~\ref{tab:evolution}), yet the mechanism
is not momentum itself but the absence of momentum continuation during broad market dislocations.
When the equal-weighted average return of the full 15-asset universe falls below $-4\%$
in a single month, the filter diverts capital to the enhanced defensive allocation before
the momentum signal has time to degrade.

This distinction matters.
A pure cross-sectional momentum strategy exits losing assets only after they have
lost sufficient relative rank; this typically lags a crash by one or two months.
In contrast, the market-breadth filter is a coincident indicator: it fires in the same
month that broad market stress materialises, well before individual asset momentum
scores reflect the change in regime.
During the Global Financial Crisis, the filter triggered six times across the
January 2008 -- June 2009 window; each trigger redirected capital to TLT and IEF,
which appreciated as investors fled equities for government bonds.
The result was a cumulative gain of $+17.64\%$ during a period when the S\&P 500
lost $-33.05\%$ (Table~\ref{tab:crisis}).

The crash filter also performed correctly in the 2020 COVID episode.
It triggered seven times over the March 2020 -- May 2023 window,
capturing the initial equity collapse (March--April 2020) and several
subsequent volatility spikes, while not over-triggering during the prolonged
2020--2021 recovery rally.
This asymmetry---defensive in crashes, offensive in recoveries---is precisely the
property required for a corporate treasury mandate.

\subsection{The Cost of Capital Protection}

Protection is not free.
The regime analysis (Table~\ref{tab:regimes}) shows that the strategy's relative
edge is concentrated in SIDEWAYS and CRISIS regimes, while the BEAR regime remains
weak and statistically fragile because it contains only nine months.
The cost of protection comes from the absolute momentum threshold
($\theta = 2\%$): when assets with positive but modest momentum scores fall below
the threshold, the portfolio may shift to defensive assets and miss part of a
sustained risk-on recovery.

Two observations mitigate this cost.
First, the strategy remains in offensive mode the majority of the time: the
overall defensive allocation rate is approximately 16\% of all months,
and 94.1\% in BULL regimes.
Second, and more fundamentally, the design objective is not to maximise
CAGR unconditionally but to satisfy a hard drawdown constraint of $-15\%$
while delivering returns above a 7\% corporate threshold.
The strategy achieves both: full-period CAGR of 11.47\% and maximum
drawdown of $-13.79\%$ throughout the entire 2008--2025 period.
The weak BEAR-regime result is the clearest actuarial premium paid
for downside protection, although that regime contains only nine observations.

\subsection{Out-of-Sample Stability}

The OOS CAGR of 12.54\% exceeds the in-sample CAGR of 10.94\%.
This result should not be over-interpreted: it reflects the specific character
of the 2020--2025 period, which combined high equity volatility
(COVID crash, 2022 inflation shock, 2025 tariff shock) with periodic
flight-to-quality episodes---exactly the conditions where the strategy's
architecture is most advantageous.

More meaningful is the absence of performance degradation.
In the TAA literature, OOS decay relative to in-sample is a standard finding
\citep{harvey2018}, driven by overfitting, data-mining bias, and regime change.
The fact that crash-filter triggers in the OOS period (9 times)
align with genuine stress events---not false positives in benign markets---
is qualitative evidence that the filter captures a persistent economic mechanism
rather than an in-sample artefact.

The robustness evidence from the threshold sensitivity analysis
(Table~\ref{tab:threshold_sensitivity}) reinforces this interpretation:
performance is broadly flat over a $\pm 1$ pp band around the selected
threshold of $-4.0\%$, implying that the chosen value is not a sharp optimum
fitted to historical crashes.

\subsection{Monte Carlo: Honest Appraisal of Uncertainty}

The stationary block bootstrap (Table~\ref{tab:montecarlo}) assesses sequencing
risk: how sensitive CAGR and maximum drawdown are to the order in which the
historically realised strategy returns arrive.
The 10th-percentile CAGR of 8.24\% remains above the 7\% corporate threshold
across adverse orderings, and 96.2\% of simulated paths exceed that threshold.
Drawdown outcomes are more path-dependent: between 30\% and 34\% of paths
(depending on block length) breach the $-15\%$ constraint, confirming that
drawdown control is a historical property of the return sequence rather than a
distributional guarantee.

The paired bootstrap provides a stronger claim on relative performance.
Across 98.2\% of simulated orderings S3.6 outperforms the 60/40 benchmark in
CAGR, and across 95.8\% in Sharpe ratio.
These figures indicate that the outperformance is not sensitive to the specific
sequence of monthly returns realised over the sample period.
The Ledoit--Wolf \citeyearpar{ledoitwolf2008} test yields $p = 0.068$ for the
Sharpe difference; with 214 monthly observations this is consistent with a
true outperformance that a longer sample would confirm at conventional
significance levels, but the evidence with the current sample remains
suggestive rather than conclusive.

This distinction matters for corporate treasury interpretation.
The crash filter provides a transparent rule for reducing exposure during
broad market stress, but it is not a statistical guarantee that every possible
ordering of returns would respect the $-15\%$ drawdown constraint.
The correct conclusion is narrower and more defensible: the strategy satisfied
the drawdown mandate historically and out-of-sample; sequencing-risk analysis
shows the outperformance is robust to reorderings of the realised returns,
while the formal Sharpe test cannot reject equality at 5\%.

\subsection{Transaction Costs and Practical Feasibility}

The base backtest reports gross performance, consistent with the
academic convention for systematic strategy evaluation.
The UCITS analysis provides a clean estimate of transaction cost impact:
using Interactive Brokers fee schedules for LSE-listed ETFs (0.05\% of order
value, minimum \$1.00 per order), commission drag is approximately 0.72 pp per
annum in the 82-transition cost window, reducing gross CAGR from 13.07\% to
12.35\% net.

Applying the same drag estimate to the full-period results yields a net CAGR
of approximately 10.75\%, which remains comfortably above the 7\% corporate
return target.
The modest drag reflects the monthly rebalancing frequency and the concentrated
three-asset portfolio, which require fewer transactions per period than
daily-rebalanced or broadly diversified strategies.
Tax treatment and custody fees are not modelled and would reduce
net returns further; their magnitude depends on entity type and jurisdiction
and is beyond the scope of this paper.

\subsection{Limitations}

Several limitations bound the interpretation of these results.

\textit{Backtest overfitting.}
All parameters---including the crash threshold $\tau = -4\%$, the absolute
momentum cutoff $\theta = 2\%$, the top-$N=7$ filter, and the triplet selection
rule---were optimised or selected within the training period.
Although the strict temporal OOS split mitigates the most direct form of
look-ahead bias, the researcher degrees of freedom in choosing the strategy
architecture are not accounted for by the OOS evaluation alone.
A fully out-of-sample validation would require live performance data, which is
not yet available for the full strategy specification.

\textit{Survivorship and selection bias.}
The ETF universe was selected retrospectively from instruments available
throughout the full sample period.
ETFs with short histories or poor liquidity that might have been considered
at the time are excluded by construction.
This introduces a mild upward bias in the estimated opportunity set.

\textit{Small BEAR regime sample.}
The BEAR regime classification contains only nine months
(Table~\ref{tab:regimes}), which is insufficient for statistical inference.
The reported CAGR of $-30.28\%$ for the strategy in that regime reflects
very few and specific observations and should not be extrapolated.

\textit{Fixed investment universe.}
The strategy does not adapt its asset universe over time.
New ETFs (factor tilts, digital assets, UCITS bond alternatives) that become
liquid during the backtest window are not eligible by construction.
Universe drift over a live multi-year implementation period is a practical
risk not captured in the simulation.
