% ============================================================
\section{Conclusion}
\label{sec:conclusion}
% ============================================================

This paper designs, backtests, and evaluates a fully automated tactical asset
allocation strategy targeting the specific constraints of corporate treasury
management: a hard maximum drawdown of $-15\%$, monthly liquidity,
no leverage or derivatives, and full automation with zero discretionary
intervention.

The strategy combines three independently motivated components.
A multi-period momentum score averages four lookback horizons (1, 3, 6, and
12 months) to reduce sensitivity to any single window and to capture trend
persistence across the cross-section of 15 diversified ETFs.
A minimum-correlation triplet selection rule builds a three-asset
equal-weight portfolio from the eligible set, exploiting the mean-variance
insight that diversification across low-correlation assets reduces portfolio
risk.
A market-breadth crash filter overrides the momentum signal whenever
the equal-weighted average return of the full universe falls below $-4\%$,
redirecting capital to long-duration treasuries or cash before
momentum-based exits can trigger.

Over the full 2008--2025 backtest period, the strategy achieves a CAGR
of 11.47\% with a Sharpe ratio of 0.974 and a maximum drawdown of $-13.79\%$,
satisfying the hard constraint throughout.
Out-of-sample performance over 2020--2025 (CAGR 12.54\%, Sharpe 1.029)
is comparable to in-sample results, providing evidence against overfitting.
A UCITS-compliant European implementation over March 2019 -- March 2026
achieves a gross CAGR of 12.71\%; in the 82-transition transaction-cost
window, net CAGR is 12.35\% after an estimated commission drag of
approximately 0.72 pp per annum.
This confirms cross-market applicability while keeping implementation costs
explicit.

During the Global Financial Crisis---the most severe stress episode in the
sample---the strategy returns $+17.64\%$ while equities lose $-33.05\%$,
demonstrating that the crash filter captures the flight-to-quality mechanism
in real time rather than in hindsight.
In CRISIS regimes, the strategy materially outperforms the 60/40 benchmark,
while the small BEAR-regime sample remains a limitation.
Return-level Monte Carlo analysis indicates that the realised strategy return
sequence is not unusually fragile (10th-percentile CAGR of 8.34\%), but
simulated drawdowns can breach the historical $-15\%$ threshold.
The stricter strategy-level bootstrap is more cautionary: when synthetic
multi-asset histories are generated and the rule is re-executed, S3.6 beats
60/40 in CAGR in only 25.6\% of simulations.
Drawdown control and benchmark outperformance should therefore be interpreted as
historical and out-of-sample properties of the realised regime sequence, not as
statistical guarantees.

These results contribute to the literature on rule-based TAA in two ways.
First, they demonstrate that a drawdown-constrained strategy historically
delivered equity-like returns over a full market cycle without recourse to leverage,
options overlays, or complex optimisation---a finding relevant for the
majority of corporate treasury functions that operate under strict
risk governance constraints.
Second, the market-breadth crash filter, adapted from the HAA framework
of \citet{keller2017} into a simpler coincident indicator, proves effective
across multiple distinct stress regimes (2008--2009, 2020, 2022, 2025),
adding to the growing evidence that breadth-based signals provide timely
information about systemic risk.

Several directions for future research follow naturally from this work.
Extending the asset universe to include additional fixed-income segments,
factor-tilt ETFs, or commodity sub-indices would test whether the
min-correlation selection rule maintains its diversification benefit
in a richer opportunity set.
A dynamic crash threshold---calibrated to the realised volatility of the
universe rather than fixed at $-4\%$---could reduce over-triggering during
high-volatility bull markets while preserving sensitivity to genuine crashes.
Finally, a prospective live implementation over a multi-year horizon
would provide out-of-sample evidence free from the researcher
degrees-of-freedom concerns that necessarily attach to all backtested strategies.

The core message is simple: a systematic, rule-based TAA strategy can satisfy
the hard risk constraints of corporate treasury while delivering returns
substantially above the passive benchmarks available in money markets
and short-duration government bonds.
The crash filter is the key differentiator; without it, the strategy
delivers returns but not the drawdown control that defines the
corporate mandate.
